Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-02 chapters/introduction/introduction.tex
some changes

\subsection{General Probabilistic Model for Geo-Calibration}
The complete camera geo-calibration includes the detection of camera
geographic location, the pose and the focal length of the camera.  We
design a general model to estimate the probability over these
geo-calibration parameters: First, we construct a scoring function to
measure the ``fitness'' between the calibration parameters and the
observation of the image. The scoring function is proportional to the
probability distribution of the camera parameters. Then we propose a
Markov Chain Monte Carlo (MCMC) sampling approach to approximate the
underlying probability distribution over the full geo-calibration of
the camera. 
Our model is a general architecture, which can take
different constraints to form the energy function. The details about
this model can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In our general model, the scoring function is defined as a linear
combination of multiple constraint functions.
In the rest of the work, We focus on developing good constraint
functions for different set of calibration parameters.

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Horizon Line and Vanishing Points:}
  We first estimate camera roll and pitch angles. Assuming the intrinsic
  parameters are known, camera roll and pitch angles can be
  derived from the horizon line position in the image. Detecting horizon
  line is easier because it is tightly related to the content/appearance
  of the scene. In our work, we create a new method using a CNN to
  estimate the prior distribution of the horizon line. We then assign
  a probability to each horizon line by measuring their consistences
  with vanishing points detected using traditional statistic methods.
  We present the algorithm details in \chapref{fasthorizon}.
  \newline

  \item \textbf{Constraint for Coarse Geographic Locations:}
  In this work, we demonstrate to estimate the camera geographic
  location with the input image.
  We provide two approaches to obtain the probability distribution over the camera
  geographic location. Most straightforwardly, our network outputs
  categorical distribution over world into a $N \times M$ bins. Better
  results can be obtained with temporal inputs (image timestamps).
  Our algorithm can also compute the probability at arbitrary
  geographic location, with lower accuracy than the straightforward
  method.
  We also demonstrate that our algorithm can learn a  geo-temporal
  feature representation of image with geographic locations and capture
  time.
  We present the algorithm details in \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and on estimating the camera geo-orientation.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to the monocular depth
  estimation methods that driven by
  the technique called {\em Reprojection
  Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
  network learns to geometrically project pixels from the overhead
  images to the ground images,
  and learns to segment the overhead images jointly. 
  When refining the camera geographic location, we compare the
  semantic layout of the ground image with those transferred from
  overhead images sampled from different locations and orientations. The
  optimal prediction is found when the semantic layouts from these
  two sources match best. For probabilistic outputs, we can also assign
  an energy score to each location and orientation combination
  according to how well the semantic layouts match to each other.
  We present the algorithm details in \chapref{crosstransf}
  \newline

>>>>

\subsection{General Probabilistic Model for Geo-Calibration}
The complete camera geo-calibration detects the camera
geographic location, pose, and focal length of the camera.  We
design a general model to estimate the probability over these
geo-calibration parameters: First, we model the relation between the
image projection of the scene and the geo-calibration parameters. This
relation is ruled by both the pin-hole model principle and the
geographic location of the camera.
We then construct a scoring function to measure the ``fitness'' between the
calibration parameters and the observation of the image. 
The scoring function is proportional to the probability distribution
of the camera parameters. We propose a Markov Chain Monte
Carlo (MCMC) sampling approach to approximate the underlying
probability distribution over the full geo-calibration of the camera.
Our model is a general architecture, which can take different
constraints to form the scoring function. The details about this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In our general model, the scoring function is defined as a linear
combination of multiple constraint functions.
In the rest of the work, We focus on developing good constraint
functions for different set of calibration parameters. Besides, we
also show our methods are able to extract high-level image features
with the help of geographic information.

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Horizon Line and Vanishing Points:}
  We first estimate camera roll and pitch angles. Assuming the intrinsic
  parameters are known, camera roll and pitch angles can be
  derived from the horizon line position in the image. Compared to
  directly detecting the camera pose, identifying horizon line is easier
  because it is tightly related to the appearance
  of the scene. In our work, we create a new method using CNN to
  estimate the prior distribution of the horizon line. We assign
  a probability to each horizon line by measuring their consistences
  with vanishing points detected using traditional statistic methods.
  We present the algorithm details in \chapref{fasthorizon}.
  \newline

  \item \textbf{Constraint for Coarse Geographic Locations:}
  In this work, we demonstrate to estimate the camera geographic
  location with the input image.
  We provide two approaches to obtain the probability distribution over the camera
  geographic location. Most straightforwardly, our network estimate the
  categorical distribution over world into a $N \times M$ bins. Better
  results can be procured with temporal inputs (image timestamps).
  Our algorithm can also compute the probability at arbitrary
  geographic location, with lower accuracy than the straightforward
  method.
  We demonstrate that our algorithm is able to learn geo-temporal
  image representations with geographic locations and capture
  time.
  We present the algorithm details in \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and on estimating the camera geo-orientation.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to the monocular depth
  estimation methods that driven by
  the technique called {\em Reprojection
  Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
  network learns to geometrically project pixels from the overhead
  images to the ground images,
  and learns to segment the overhead images jointly. 
  When refining the camera geographic location, we compare the
  semantic layout of the ground image with those transferred from
  overhead images sampled from different locations and orientations. The
  optimal prediction is found when the semantic layouts from these
  two sources match best. For probabilistic outputs, we assign
  a score to each location and orientation setting,
  based on how well the semantic layouts match to each other.
  We present the algorithm details in \chapref{crosstransf}
  \newline
